### 2018-08-01 doc/plos/text/manuscript.tex
add accuracy_vs_sensors figure
Some slight rewording, add new subsubsections.

In total, we produced 29,103 nowcasts for 75 US locations across 397 weeks
spanning 2010w45--2018w24. Locations include the US as a whole, the 10 HHS
regions, the 9 census divisions, the 50 states, the District of Columbia,
Puerto Rico, the US Virgin Islands, New York City, and New York state
\textit{excluding} New York City. Fig~\ref{figure_all_nowcasts} shows a
time-series comparison of all nowcasts with ground truth. Although these
nowcasts were computed in retrospect, models were trained using only data that
would have been available at the time. Namely, whenever possible, preliminary
values of wILI were used in place of final values.

@@

>>>>

In total, we produced 29,103 nowcasts for 75 US locations across 397 weeks
spanning 2010w45--2018w24. Locations include the US as a whole, the 10 HHS
regions, the 9 census divisions, the 50 states, the District of Columbia,
Puerto Rico, the US Virgin Islands, New York City, and New York state
\textit{excluding} New York City. Fig~\ref{figure_all_nowcasts} shows a
time-series comparison of all nowcasts with ground truth. Although these
nowcasts were computed in retrospect, models were trained whenever possible
using only data that would have been available at the time. For any given week,
preliminary values of wILI (when known) were used in place of final values, and
data from future weeks was held out.

@@

\subsection*{Accuracy relative to data sources}

The error (measured in MAE and RMSE) of nowcasts of ILI for the US as a whole
relative to the same error for each data source are shown in
Fig~\ref{figure_accuracy_vs_sensors}.

\begin{figure}[!ht]
  \maybeincludegraphics{accuracy_vs_sensors}
  \caption{
    {\bf Nowcast error compared with sensor error.}
    TODO: explain this
  }
  \label{figure_accuracy_vs_sensors}
\end{figure}

\subsection*{Accuracy relative to baselines}

TODO (python3 analyze.py metrics)
